Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.qmd
fixed inconsistent timestamp spelling

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

@@

**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a time stamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.**

@@

**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any time stamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.**

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-divisions
#| tbl-cap: "Summary and description of variables in our divisions data file"
tibble("Variable" = c("date",
                      "div_num",
                      "time.stamp",
                      "num.votes_AYES",
                      "num.votes_NOES",
                      "num.votes_PAIRS",
                      "names_AYES",
                      "names_NOES",
                      "names_PAIRS",
                      "result"),
       "Description" = c("Sitting day",
                         "Index for each division parsed for that sitting day",
                         "Time stamp associated with each division",
                         "Number of votes in the affirmative",
                         "Number of votes in the negative",
                         "Number of votes in pairs",
                         "List of the names of Members who voted in the affirmative",
                         "List of the names of Members who voted in the negative",
                         "List of the names of Members who votes in pairs",
                         "Voting result")) |> 
  kable(booktabs=T) %>% 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
```

@@

**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all time stamps in our database which do not match the correct "HH:MM:SS" format. We found a total of 88 incorrectly formatted time stamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g. "NaN:28:00" or "09:NaN:00"), as well as timestamps with a third digit in the minute component (e.g. "09:497:00" or "13:445:00"). We took a random sample of 25% of these incorrectly formatted timestamps, and manually checked whether or not they were transcribed as such in the original XML Hansard transcript. We found that every improperly formatted timestamp in our random sample was in fact transcribed as such in its original XML file, meaning these bugs are the result of a transcription error, rather than an error resulting from our data parsing or cleaning code. As such, we have left these timestamps in their originally transcribed format in our database.**

>>>>

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as timestamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

@@

**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.**

@@

**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.**

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-divisions
#| tbl-cap: "Summary and description of variables in our divisions data file"
tibble("Variable" = c("date",
                      "div_num",
                      "time.stamp",
                      "num.votes_AYES",
                      "num.votes_NOES",
                      "num.votes_PAIRS",
                      "names_AYES",
                      "names_NOES",
                      "names_PAIRS",
                      "result"),
       "Description" = c("Sitting day",
                         "Index for each division parsed for that sitting day",
                         "Timestamp associated with each division",
                         "Number of votes in the affirmative",
                         "Number of votes in the negative",
                         "Number of votes in pairs",
                         "List of the names of Members who voted in the affirmative",
                         "List of the names of Members who voted in the negative",
                         "List of the names of Members who votes in pairs",
                         "Voting result")) |> 
  kable(booktabs=T) %>% 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
```

@@

**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all timestamps in our database which do not match the correct "HH:MM:SS" format. We found a total of 88 incorrectly formatted timestamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g. "NaN:28:00" or "09:NaN:00"), as well as timestamps with a third digit in the minute component (e.g. "09:497:00" or "13:445:00"). We took a random sample of 25% of these incorrectly formatted timestamps, and manually checked whether or not they were transcribed as such in the original XML Hansard transcript. We found that every improperly formatted timestamp in our random sample was in fact transcribed as such in its original XML file, meaning these bugs are the result of a transcription error, rather than an error resulting from our data parsing or cleaning code. As such, we have left these timestamps in their originally transcribed format in our database.**

### 2023-07-06 paper/paper-nature-revised.tex
fixed inconsistent timestamp spelling

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, interior hidden, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a time stamp.
Therefore, we took the first available page number child-node for each
debate or sub-debate node to be the one we included in our dataset.
After summarizing, these topics can be added to the main text by
joining, and example code is provided in the README.}

@@

\textbf{In the Hansard XML files, divisions data are structured outside
of the \texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in Section~\ref{sec-diff} naturally allowed for much
of the divisions data to be added to our resulting files for 1998 to
March 2011, however the parsing scripts used for May 2011 to September
2022 Hansard did not. To supplement our database and in an effort to
fill this divisions data gap, we created an additional file containing
all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any time stamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}division\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.}

@@

\centering
\begin{tabular}{ll}
\toprule
Variable & Description\\
\midrule
date & Sitting day\\
div\_num & Index for each division parsed for that sitting day\\
time.stamp & Time stamp associated with each division\\
num.votes\_AYES & Number of votes in the affirmative\\
num.votes\_NOES & Number of votes in the negative\\
\addlinespace
num.votes\_PAIRS & Number of votes in pairs\\
names\_AYES & List of the names of Members who voted in the affirmative\\
names\_NOES & List of the names of Members who voted in the negative\\
names\_PAIRS & List of the names of Members who votes in pairs\\
result & Voting result\\
\bottomrule
\end{tabular}
\end{table}

@@

\textbf{The fourth test is designed to detect issues in timestamp
formatting in the data, by detecting all time stamps in our database
which do not match the correct ``HH:MM:SS'' format. We found a total of
88 incorrectly formatted time stamps, with common issues such as the
``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or
``09:NaN:00''), as well as timestamps with a third digit in the minute
component (e.g.~``09:497:00'' or ``13:445:00''). We took a random sample
of 25\% of these incorrectly formatted timestamps, and manually checked
whether or not they were transcribed as such in the original XML Hansard
transcript. We found that every improperly formatted timestamp in our
random sample was in fact transcribed as such in its original XML file,
meaning these bugs are the result of a transcription error, rather than
an error resulting from our data parsing or cleaning code. As such, we
have left these timestamps in their originally transcribed format in our
database.}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, frame hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as timestamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a timestamp. Therefore,
we took the first available page number child-node for each debate or
sub-debate node to be the one we included in our dataset. After
summarizing, these topics can be added to the main text by joining, and
example code is provided in the README.}

@@

\textbf{In the Hansard XML files, divisions data are structured outside
of the \texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in Section~\ref{sec-diff} naturally allowed for much
of the divisions data to be added to our resulting files for 1998 to
March 2011, however the parsing scripts used for May 2011 to September
2022 Hansard did not. To supplement our database and in an effort to
fill this divisions data gap, we created an additional file containing
all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any timestamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}division\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.}

@@

\centering
\begin{tabular}{ll}
\toprule
Variable & Description\\
\midrule
date & Sitting day\\
div\_num & Index for each division parsed for that sitting day\\
time.stamp & Timestamp associated with each division\\
num.votes\_AYES & Number of votes in the affirmative\\
num.votes\_NOES & Number of votes in the negative\\
\addlinespace
num.votes\_PAIRS & Number of votes in pairs\\
names\_AYES & List of the names of Members who voted in the affirmative\\
names\_NOES & List of the names of Members who voted in the negative\\
names\_PAIRS & List of the names of Members who votes in pairs\\
result & Voting result\\
\bottomrule
\end{tabular}
\end{table}

@@

\textbf{The fourth test is designed to detect issues in timestamp
formatting in the data, by detecting all timestamps in our database
which do not match the correct ``HH:MM:SS'' format. We found a total of
88 incorrectly formatted timestamps, with common issues such as the
``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or
``09:NaN:00''), as well as timestamps with a third digit in the minute
component (e.g.~``09:497:00'' or ``13:445:00''). We took a random sample
of 25\% of these incorrectly formatted timestamps, and manually checked
whether or not they were transcribed as such in the original XML Hansard
transcript. We found that every improperly formatted timestamp in our
random sample was in fact transcribed as such in its original XML file,
meaning these bugs are the result of a transcription error, rather than
an error resulting from our data parsing or cleaning code. As such, we
have left these timestamps in their originally transcribed format in our
database.}
